The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-05-01 article.tex
Use v1.4.19 everywhere
A bit more textual variance

  A reference implementation, \texttt{CDKAtomTypeMatcher}, has been
  written that perceives these atom types, and validates the
  perception automatically against the properties defined by the
  ontology.  This class handles a variety of types of missing
  information, as commonly resulting from various (file) formats; for
  example, it can handle undefined hydrogen counts and undefined
  double bond positions if hybridization information is provided
  instead.  That makes the perception code flexible but also more
  complex. Alternative algorithms for atom typing have not been
  explored. This reference implementation can be used on a single
  atom:

@@

The CDK library is now mostly written that it no longer depends on a specific
implementation of the \texttt{IChemObjectBuilder}, allowing the user of the
CDK to select a builder suitable to their software. Therefore, if software
depends on event passing, then the \texttt{DefaultChemObjectBuilder} can be
used, in most cases this isn't needed and the \texttt{SilentChemObjectBuilder} 
is preferred resulting in a typical speed up of 10\% to 20\%:

@@

Benchmark  & \multicolumn{2}{c}{Data Set} & \multicolumn{3}{c}{CDK 1.4.19} & \multicolumn{3}{c}{CDK \cdkversion{}} & Improvement \\

>>>>

  A reference implementation, \texttt{CDKAtomTypeMatcher}, has been
  written in such a way that perceives these atom types, and validates the
  perception automatically against the properties defined by the
  ontology.  This class handles a variety of types of missing
  information, as commonly resulting from various (file) formats; for
  example, it can handle undefined hydrogen counts and undefined
  double bond positions if hybridization information is provided
  instead.  That makes the perception code flexible but also more
  complex. Alternative algorithms for atom typing have not been
  explored. This reference implementation can be used on a single
  atom:

@@

The CDK library is now mostly refactored and no longer depends on a specific
implementation of the \texttt{IChemObjectBuilder}, allowing the user of the
CDK to select a builder suitable to their software. Therefore, if software
depends on event passing, then the \texttt{DefaultChemObjectBuilder} can be
used, in most cases this isn't needed and the \texttt{SilentChemObjectBuilder} 
is preferred resulting in a typical speed up of 10\% to 20\%:

@@

Benchmark  & \multicolumn{2}{c}{Data Set} & \multicolumn{3}{c}{CDK v1.4.19} & \multicolumn{3}{c}{CDK \cdkversion{}} & Improvement \\
